Analysis of cloud enhancement events in a 30-year record of global solar irradiance at Thessaloniki, Greece

### 2024-09-06 article/article.Rmd
Commit 2024-09-06 20:14

First, we evaluated the performance of the modelled $\text{GHI}_\text{ref}$ in
relation to the measured GHI for different levels of atmospheric clearness, by using
in the RTM the monthly climatological AOD and WC, less their respective standard
deviations.
<!--
$\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$
($\text{GHI}_\text{CSm}$).
-->
These values represent typical atmospheres in Thessaloniki with lower than average
load of aerosols and humidity, which are the main factors that attenuate the GHI,
excluding clouds.  With this approach the simulated $\text{GHI}_\text{ref}$ should be
generally greater than the measured GHI when aerosols are more abundant.  To
compensate for this, we defined the following threshold $E$ to compare the
measured $\text{GHI}$: 
<!--
($`r 100*(C4_cs_ref_ratio-1)`\,\%$)
with an additional constant offset of
$`r C4_GLB_diff_THRES`\,\text{W}/\text{m}^2$,
as described in Equation\nobreakspace\ref{eq:CE4}.
-->
\begin{equation}
\text{CE} : E > `r C4_GLB_diff_THRES` + `r C4_cs_ref_ratio` \cdot \text{GHI}_\text{ref} \,\,[\text{W}/\text{m}^2] \label{eq:CE4}
\end{equation}

@@

<!--
- can follow for clear days
- the most important are the thresholds
- model have to be uniform on clear days
- the level is adjusted by the threshold 
- the effect of the sza uniform
-->

@@

An example of CE identification for a selected day is given in the
Figure\nobreakspace{}\ref{fig:example-day}, where the daily course of the cloud-free
reference irradiance and the CE and ECE identification thresholds are shown along
with the actual GHI measurements.  In addition, we provide an example scatter plot
between the measured and the modeled cloud-free irradiance for one year, where the CE
and ECE events are clearly grouped above the threshold of irradiance
(Figure\nobreakspace{}\ref{fig:example-year}).

>>>>

First, we evaluated the performance of the modelled $\text{GHI}_\text{ref}$ in
relation to the measured GHI for different levels of atmospheric clearness, by using
in the RTM the monthly climatological AOD and WC, less their respective standard
deviations.
<!--
$\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$
($\text{GHI}_\text{CSm}$).
-->
These values represent typical atmospheres in Thessaloniki with lower than average
load of aerosols and humidity, which are the main factors that attenuate the GHI,
excluding clouds.  With this approach the simulated $\text{GHI}_\text{ref}$ should be
generally greater than the measured GHI when aerosols are more abundant.  To
compensate for this, we defined the following threshold $E$ to compare the
measured $\text{GHI}$:
\begin{equation}
\text{CE} : E > `r C4_GLB_diff_THRES` + `r C4_cs_ref_ratio` \cdot \text{GHI}_\text{ref} \,\,[\text{W}/\text{m}^2] \label{eq:CE4}
\end{equation}

@@

@@

An example of the identification of CE events for a selected day is given in the
Figure\nobreakspace{}\ref{fig:example-day}, where the daily course of the cloud-free
reference irradiance and the CE and ECE identification thresholds are shown along
with the actual GHI measurements.  In addition, we provide an example scatter plot
between the measured and the modeled cloud-free irradiance for one year, where the CE
and ECE events are clearly grouped above the threshold of irradiance
(Figure\nobreakspace{}\ref{fig:example-year}).
